Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs

### 2020-06-02 main.tex
More related work, and remarks from Denis

\begin{abstract}
We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned along the way (adaptive), in a critical setting where failures must be prevented (robust). This problem has been studied from different perspectives by different communities. However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation and tracking tasks only. In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting. Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions. Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
\end{abstract}

@@

Despite the recent successes of Reinforcement Learning \citep[e.g.][]{mnih2015humanlevel,Silver1140}, it has hardly been applied in real industrial issues. This could be attributed to two undesirable properties which limit its practical applications. First, it depends on a tremendous amount of interaction data that cannot always be simulated. This issue is alleviated by model-based methods -- which we consider in this work -- that often benefit from better sample efficiencies than their model-free counterparts. Second, it relies on trial-and-error and random exploration. In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time. 
This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
Since experiencing failures is out of question, the only way to prevent them from the outset is to rely on some sort of prior knowledge. In this work, we assume that the system dynamics are partially known, in the form of a linear differential equation with unknown parameters and inputs. More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
\end{equation}
where the parameter vector $\theta$ in the state matrix $A(\theta)\in\Real^{p\times p}$ belongs to a compact set $\Theta \subset \Real^d$. The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known. We also assume having access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$. We argue that this structure assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning. Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model. We adopt a data-driven scheme to estimate the parameters more accurately as we interact with the true system. Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error between the learned and true dynamics, which can dramatically degrade control performances \citep{Schneider1997}. %It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.

To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} $\cC_{[N],\delta} \subset \Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
\begin{align}
\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta,
\label{eq:confidence}
\end{align}
where $\delta\in(0,1)$. In \Cref{sec:estimation}, having observed a history $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$ of transitions, our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the least-square estimator to our setting of feature matrices, rather than feature vectors.

The \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} aims to maximise the worst-case outcome with respect to this confidence region $\cC_{[N],\delta}$:
\begin{equation}
\label{eq:robust-control}
\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
\end{equation}
$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$ within the given admissible bounds $[\underline\omega(t),\overline\omega(t)]$. Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard if the reward $R$ has a simple form. With arbitrary functions $R$, we cannot hope to derive an explicit solution.
In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically. In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}. This predictor takes the information on the current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
\begin{equation}
\label{eq:inclusion-property}
\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
\end{equation}

Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective is intractable. In \Cref{sec:control}, facing a sequential decision problem with continuous states, we turn to the literature of tree-based planning algorithms. Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite space $\cA$. Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine: $u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.$ For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$. This discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
However, tree-based planning algorithms are designed for a single known generative model rather than a confidence region for the system dynamics. Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictor \eqref{eq:inclusion-property} to define a pessimistic reward. In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:control-error}. This is the first result of this kind for maximin control with generic costs to the best of our knowledge. \Cref{alg:full} shows the full integration of the three procedures of estimation, prediction and control.

@@

\begin{algorithm}[tb]
	\caption{Robust Estimation, Prediction and Control}
	\label{alg:full}
	\begin{algorithmic}
		\STATE {\bfseries Input:} confidence level $\delta$, structure $(A,\phi)$, reward $R$, $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
		\FOR{$N = 0,1,2,\dots$} 
		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
		\FOR{each planning step $k\in[K]$}
		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}

		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$(\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
		\ENDFOR
		\STATE Execute the control $u_{N+1}$, and add the observed transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

The control of uncertain systems is a long-standing problem, to which a vast body of literature is dedicated. Existing work is mostly concerned with the problem of \emph{stabilisation} around a fixed reference state or trajectory, including approaches such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997} or system-level synthesis \citep{Dean2017,Dean2018}. This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014}. The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep[e.g.][]{Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}. Yet, we argue that many tasks cannot be framed as (robust) stabilisation problems (e.g. obstacle avoidance) and are better addressed with the minimax control objective, which can allow more flexible goal formulations. Minimax control has mostly been studied in two particular instances.

@@

\textbf{Linear dynamics and quadratic costs} ~~ Several approaches have been proposed for cumulative regret minimisation in the LQ problem. In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation. \citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret. Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result. Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}. However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes. The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance. 
Our work differs in that it addresses arbitrary bounded costs, rather than quadratic costs only.

@@

\begin{assumption}[Sub-Gaussian Noise]
\label{assumpt:gaussian-noise}
At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
$
    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}.
$
\end{assumption}
For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.
%Note that \Cref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.

@@

\paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against. We use local bounds that each holds with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.

>>>>

\begin{abstract}
We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned along the way (adaptive), in a critical setting where failures must be prevented (robust). This problem has been studied from different perspectives by different communities. However, the existing theory deals only with the case of quadratic costs (the LQ problem), which limits applications to stabilisation and tracking tasks only. In order to handle more general (non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting. Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions. Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
\end{abstract}

@@

Despite the recent successes of Reinforcement Learning \citep[e.g.][]{mnih2015humanlevel,Silver1140}, it has hardly been applied in real industrial issues. This could be attributed to two undesirable properties which limit its practical applications. First, it depends on a tremendous amount of interaction data that cannot always be simulated. This issue can be alleviated by model-based methods -- which we consider in this work -- that often benefit from better sample efficiencies than their model-free counterparts. Second, it relies on trial-and-error and random exploration. In order to overcome these shortages, and motivated by the path planning problem for a self-driving car, in this paper we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time. 
This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
Since experiencing failures is out of question, the only way to prevent them from the outset is to rely on some sort of prior knowledge. In this work, we assume that the system dynamics are partially known, in the form of a linear differential equation with unknown parameters and inputs. More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
\end{equation}
where the parameter vector $\theta$ in the state matrix $A(\theta)\in\Real^{p\times p}$ belongs to a compact set $\Theta \subset \Real^d$. The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known. We also assume having access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$. We argue that this structure assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning. Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model. We adopt a data-driven scheme to estimate the parameters more accurately as we interact with the true system. Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error between the learned and true dynamics, which can dramatically degrade control performances \citep{Schneider1997}. %It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.

To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{[N],\delta}$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
\begin{align}
\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta,
\label{eq:confidence}
\end{align}
where $\delta\in(0,1)$. In \Cref{sec:estimation}, having observed a history $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$ of transitions, our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the least-square estimator to our setting of feature matrices, rather than feature vectors.

The \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} aims to maximise the worst-case outcome with respect to this confidence region $\cC_{[N],\delta}$:
\begin{equation}
\label{eq:robust-control}
\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
\end{equation}
$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$ within the given admissible bounds $[\underline\omega(t),\overline\omega(t)]$. Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard if the reward $R$ has a simple form. However, without a restriction on the shape of functions $R$, we cannot hope to derive an explicit solution.
In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically. In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}. For any $N\in\Natural$, his predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{[N],\delta}$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
\begin{equation}
\label{eq:inclusion-property}
\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
\end{equation}

Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective is intractable. In \Cref{sec:control}, facing a sequential decision problem with continuous states, we turn to the literature of tree-based planning algorithms. Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite space $\cA$. Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine: $u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.$ For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$. This discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
However, tree-based planning algorithms are designed for a single known generative model rather than a confidence region for the system dynamics. Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictions \eqref{eq:inclusion-property} to define a pessimistic reward. In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:control-error}. This is the first result of this kind for maximin control with generic costs to the best of our knowledge. \Cref{alg:full} shows the full integration of the three procedures of estimation, prediction and control.

@@

\begin{algorithm}[tb]
	\caption{Robust Estimation, Prediction and Control}
	\label{alg:full}
	\begin{algorithmic}
		\STATE {\bfseries Input:} confidence level $\delta$, structure $(A,\phi)$, reward $R$, $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
		\FOR{$N = 0,1,2,\dots$} 
		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
		\FOR{each planning step $k\in\{N,\dots,N+K\}=N+[K]$}
		\STATE $[\underline{x}_{k+1}, \overline{x}_{k+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}

		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$(\underline{R_{k+1}}([\underline{x}_{k+1}, \overline{x}_{k+1}]))$.  \eqref{eq:opd}
		\ENDFOR
		\STATE Execute the recommended control $u_{N+1}$, and add the transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

The control of uncertain systems is a long-standing problem, to which a vast body of literature is dedicated. Existing work is mostly concerned with the problem of \emph{stabilisation} around a fixed reference state or trajectory, including approaches such as $\cH_\infty$ control \citep[][]{Basar1996}, sliding-mode control \citep{Lu1997} or system-level synthesis \citep{Dean2017,Dean2018}. This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014,Amos2018}, but lack guarantees. The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: the state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep{Fukushima2007,Adetola2009,Aswani2013,Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}. %, their adaptive versions take also into account the possible parametric model uncertainty
Yet, many tasks cannot be framed as stabilisation problems (e.g. obstacle avoidance) and are better addressed with the minimax control objective, which can allow more flexible goal formulations. Minimax control has mostly been studied in two particular instances.

@@

\textbf{Linear dynamics and quadratic costs} ~~ Several approaches have been proposed for cumulative regret minimisation in the LQ problem. In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation. The results of 	\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret. Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result. Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}. However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes. The work of \citet{Dean2017} is close to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance. Our work differs in that it addresses a generic shape cost. 
Another work of interest is \citep{Rosolia2019} where worst-case generic costs are considered. However, they assume the knowledge of the dynamics, and their rollout-based solution only produces inner-approximations and do not yield any guarantee. In this paper, interval prediction is used to produce oversets, while a near-optimal control is found using a tree-based planning procedure.

@@

\begin{assumption}[Sub-Gaussian Noise]
\label{assumpt:gaussian-noise}
At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
$
    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}.
$
\end{assumption}
For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.

\textbf{Remark} ~ In the objective \eqref{eq:robust-control}, we use local bounds  $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ that hold with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
%Note that \Cref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.

@@
